Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-10-13 analysis/paper/paper.Rmd
Correct spelling of "Swath"

To understand where we stand as a discipline regarding open science and reproducible research, we surveyed a broad selection of articles to represent a wide swathe of publications to evaluate our collective status.
We hand-picked 21 journals which we felt represented research publications in the field of plant pathology (Table \@ref(tab:journals)) that encompassed a range of subject matter foci, applied and fundamental work, country of origin and ranking metrics, *e.g.*, quartile range or citation index, to represent the discipline.
The aim was to gather as complete an overview of the status of computational reproducibility in plant pathology journals as possible and avoid bias in the findings by skewing towards high-impact journals that may have a greater influence.
From those 21 journals we randomly selected 450 articles published from 2012 to 2021.
Using R [@RCT2022], two lists were created, the first was a list of the 21 journals and the second was a list of the evaluators that were evaluating the articles for reproducibility.
Initially there were four evaluators, later a fifth was added and the list was recreated.
There were three evaluation events that took place to increase the yearly coverage of the evaluations.
During each scoring event, each evaluator was randomly assigned 50 unique articles to evaluate during an evaluation event.

>>>>

To understand where we stand as a discipline regarding open science and reproducible research, we surveyed a broad selection of articles to represent a wide swath of publications to evaluate our collective status.
We hand-picked 21 journals which we felt represented research publications in the field of plant pathology (Table \@ref(tab:journals)) that encompassed a range of subject matter foci, applied and fundamental work, country of origin and ranking metrics, *e.g.*, quartile range or citation index, to represent the discipline.
The aim was to gather as complete an overview of the status of computational reproducibility in plant pathology journals as possible and avoid bias in the findings by skewing towards high-impact journals that may have a greater influence.
From those 21 journals we randomly selected 450 articles published from 2012 to 2021.
Using R [@RCT2022], two lists were created, the first was a list of the 21 journals and the second was a list of the evaluators that were evaluating the articles for reproducibility.
Initially there were four evaluators, later a fifth was added and the list was recreated.
There were three evaluation events that took place to increase the yearly coverage of the evaluations.
During each scoring event, each evaluator was randomly assigned 50 unique articles to evaluate during an evaluation event.
